\documentclass[a4paper,9pt]{article}
\usepackage[margin=0.7in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}

\renewcommand{\baselinestretch}{1.1}

\titleformat{\section}{\bfseries\large\vspace{-1ex}}{}{0em}{}
\titleformat{\subsection}{\bfseries\vspace{-1ex}}{}{0em}{}
\titlespacing*{\section}{0pt}{2ex}{1ex}
\titlespacing*{\subsection}{0pt}{1ex}{0.5ex}

\setlist[itemize]{noitemsep, topsep=0pt, left=1em}
\setlength{\parskip}{0em}
\setlength{\parindent}{0em}

\newcommand{\sectionrule}{
    \vspace{0.5em}
    \hrule height 0.4pt
    \vspace{0.5em}
}

\begin{document}

% Education Section
\section*{\Large Education}
\sectionrule
\noindent
\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}} l r}
\textbf{University of Waterloo} & Xxx,Xxx \\
\textit{Honors Bachelor of Science in Physics, Minor in Computing} & \textit{Xxx,Xxx - Xxx,Xxx} \\
\end{tabular*}

\vspace{0.8em}

% Experience Section
\section*{\Large Experience}
\sectionrule
\noindent
\textbf{Ernst \& Young LLP} \hfill Xxx,Xxx \\
Data Science Assurance Associate \hfill \textit{Xxx,Xxx - Xxx,Xxx}
\begin{itemize}
    \item Developed an automated review platform utilizing predictive coding and topic modeling, reducing review costs and time.
    \item Conducted R\&D on classification models and text data mining for fraud detection utilizing Python, scikit-learn, and Tableau.
    \item Integrated cloud-based solutions for enhanced data processing and storage efficiency.
\end{itemize}

\vspace{0.8em}

\noindent
\textbf{x} \hfill Xxx,Xxx \\
Multiple Data Science Projects for USA Clients \hfill \textit{Xxx,Xxx - Xxx,Xxx}
\begin{itemize}
    \item Implemented sentiment analysis and time-series analysis on survey data for motor vehicle customer reviews using NLP techniques.
    \item Designed a chatbot for customer query management using Python, JavaScript, and SQL Server.
    \item Developed a Fraud Analytic Platform enabling advanced data analytics for ERP systems.
\end{itemize}

\vspace{0.8em}

% Projects Section
\section*{\Large Project}
\sectionrule
\noindent
\textbf{Fraud Analytic Platform} | \textit{x} \hfill \textit{Xxx,Xxx - Xxx,Xxx}
\begin{itemize}
    \item Engineered a dynamic platform for fraud detection employing advanced analytics, resulting in a XX\% reduction in detection time using HTML, SQL Server, and JavaScript.
\end{itemize}

\vspace{0.8em}

\noindent
\textbf{Chatbot Development} | \textit{x} \hfill \textit{Xxx,Xxx - Xxx,Xxx}
\begin{itemize}
    \item Developed a customer service chatbot enhancing query handling efficiency by XX\% through Python and SQL Server integration.
\end{itemize}

\vspace{0.8em}

\section*{\Large Technical Skills}
\sectionrule
\noindent
\textbf{Languages}: Python, SQL, JavaScript \\
\textbf{Frameworks}: Sentiment Analysis, Topic Modeling, NLP \\
\textbf{Databases}: MySQL, Elasticsearch, Tableau

\end{document}